### 2023-12-05 manuscript.tex
Simplified title page

\textbf{Title:} Evolutionary analyses of IDRs reveal widespread signals of conservation

\textbf{Authors:} Marc Singleton\textsuperscript{1,*}, Michael Eisen\textsuperscript{1,2}

\textbf{Author addresses:}\\
1 Howard Hughes Medical Institute, UC Berkeley, Berkeley, CA 94720, USA\\
2 Department of Molecular and Cell Biology, UC Berkeley, Berkeley, CA 94720, USA

\textbf{Corresponding author:}\\
* Howard Hughes Medical Institute, UC Berkeley, Berkeley, CA 94720, USA. Email: marcsingleton@berkeley.edu

>>>>

Evolutionary analyses of IDRs reveal widespread signals of conservation

Marc Singleton\textsuperscript{1,*}, Michael Eisen\textsuperscript{1,2}

1 Howard Hughes Medical Institute, UC Berkeley, Berkeley, CA 94720, USA\\
2 Department of Molecular and Cell Biology, UC Berkeley, Berkeley, CA 94720, USA

* Corresponding author\\
Email: marcsingleton@berkeley.edu
